The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-01-08 Ben_Manuscripts/transport/Outline.tex
Up to date methods for CTRW simulation

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}

@@

  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item See supporting info for water equilibration simulation data.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimzation.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data using long simulations, on the order of
	1 microsecond, with pressure controlled by the Parrinello-Rahman barostat.
  \end{itemize}

@@

  A continuous time random walk (CTRW) is a stochastic anomalous diffusion
  process characterized by a distribution of hop lengths and dwell times.
  \begin{itemize}
	\item The MSD for an anomalous diffusion process is of the form $$t^\alpha$$
	\item A value of $\alpha < 1$ tells us that the molecules exhibits subdiffusion
	\item Subdiffusive, non-ergodic processes with uncorrelated steps help distinguish 
	a CTRW from other anomalous subdiffusive process such as fraction brownian motion 
	and random walks on a fractal.
	\item See supporting info for proof of the system's non-ergodicty and uncorrelated steps.
  \end{itemize}

  We fit our data to a CTRW model by using our data in order to construct 
  dwell time and hop length distributions.
  \begin{itemize}
	\item We use the \texttt{ruptures} python package in order to identify
	breakpoints in solute trajectories. (See Supporting Information for more
	details on chosen parameters. i.e. type of cost function, cost function penalty
	tolerance, number of dimensions used)
	\item We have limited data, so we attempted to approximate these distributions
	with known continuous probability densities.
	\item Incorporates effects of `aging' since it samples long dwell times
	\item For solutes in our system the distribution of hop lengths is
	well-represented by a Gaussian distribution 
	\item The distribution of dwell	times is expected to fit a heavy tailed distribution: 
  \end{itemize}

  \begin{equation}
	Ax^{(-1 - \alpha)}
  \end{equation}

  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
  magnitude longer than our molecular simulations. 
  \begin{itemize}
	\item We constructed trajectories by generating sequences of dwell times 
        and hop lengths randomly sampled from our fit distributions.
	\item For time scales much greater than the characteristic time of our
	dwell time distribution, solutes exhibit Brownian motion. 
	\item The MSD curve becomes linear
	\item We fit a line to the MSD curve and used the Einstein relationship
	to relate its slope to the macroscopic diffusion coefficient.
	\item We found convergence of the value of the diffusion coefficient 
	calculated in this way afer x steps (See Supporting Information)
  \end{itemize}

@@

  We quantified the coordination of solutes with surrounding molecules and
  functional groups in two ways.
  \begin{itemize}
	\item By counting the number of coordinated molecules to a given solute
	based on a distance cut-off. Gives frame-by-frame information. 
	\item By averaging 3D spherical radial distribution function calculated for
	each solute.
  \end{itemize}

@@

  \subsection{Macroscopic Diffusion Coefficients}

  \subsubsection{Simulated Predictions}\label{section:D_macro}

@@

  Overwhelming amount of water in 10 wt\% system makes hydrogen bonding
  competitive between head groups and water.

@@

  \clearpage
  \bibliography{llc}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}

@@

  %MRS: may need to discuss the fact that the amount of water present in the tails may 
  %MRS: or may not be experimentally consistent; but if we don't put it in, the results will 
  %MRS: not be thermodynamically consistent, which will give issues with measurements and calculations.
  %MRS2: hopefully, some experiments could let us know about different diffusion regimes . . . 
  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item See supporting info for water equilibration simulation data.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes (reference
	to supporting information to show low degree of interaction)
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimzation.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data using long simulations, on the order of
	1 microsecond
	\item .mdp files are in the supporting information % with pressure controlled by the Parrinello-Rahman barostat.
  \end{itemize}

@@

  A continuous time random walk (CTRW) is a stochastic anomalous diffusion
  process characterized by a distribution of hop lengths and dwell times.
  \begin{itemize}
	\item The MSD for an anomalous diffusion process is of the form
	\begin{equation} 
	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
	\end{equation} 
	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
	generalized diffusion coefficient. 
	\item A value of $\alpha < 1$ indicates a subdiffusive process.
	\item Subdiffusive, non-ergodic processes with uncorrelated steps distinguish 
	a CTRW from other anomalous subdiffusive process such as fractional brownian motion 
	and random walks on a fractal.~\cite{meroz_toolbox_2015}
	\item See supporting info for proof of the system's non-ergodicty and uncorrelated steps.
  \end{itemize}

  We obtained maximum likelihood estimates (MLE) of the parameters used to fit our
  emperical dwell and hop length distributions to analytical functions.
  \begin{itemize}
	\item We used the \texttt{ruptures} python package in order to identify
	breakpoints in solute trajectories. (See Supporting Information for more
	details on chosen parameters. i.e. type of cost function, cost function penalty
	tolerance, number of dimensions used)
	\item The corresponding hop lengths and dwell times between break points were 
	used to construct emperical distributions.
	\item For solutes in our system the distribution of hop lengths is
	well-represented by a Gaussian distribution (Which has been often used in
	literature)
	\item The maximum likelihood estimate of Gaussian parameters is given simply
	by the mean and standard deviation of the emperical data.
	~\cite{metzler_random_2000,metzler_anomalous_2014,neusius_subdiffusion_2009} 
	\item The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
	distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
	\item Because we are limited to taking measurements at discrete values
	dictated by the output frequency of our simulation trajectories, we fit the
	emperical dwell times to a discrete power law distribution whose maximum
	likelihood $\alpha$ parameter we calculated by maximizing the following
	likelihood function: 
        \begin{equation}
	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
	\beta\sum_{i=1}^{n} \text{ln}~x_i 
	\label{eqn:powelaw_likelihood}
	\end{equation}
	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
	where $x_{min}$ is the smallest measured value of
	$x_i$.~\cite{clauset_power-law_2009} 
	%\item Incorporates effects of `aging' since it samples long dwell times
  \end{itemize}

  %BJC: not sure following explanation is necessary. Could put thesis statement
  % in previous paragraph.
  We generated distributions of parameters for the dwell time and hop length
  distributions using statistical bootstrapping.
  \begin{itemize}
	\item For each type of distribution, we randomly selected $n$ data points from the emperical
	distribution with replacement.
	\item We repeated the fitting procedure described above for each of 200 bootstrap trials.
  \end{itemize}

%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
%  magnitude longer than our molecular simulations.
  We simulated trajectories order of magnitude longer than our molecular simulations. 
  \begin{itemize}
	\item We constructed 10000, 10000 timestep trajectories by generating
	sequences of dwell times and hop lengths randomly sampled from the appropriate
	distributions.
	\item For each trajectory, the parameters used to define each distribution were
	randomly drawn from the bootstrapped parameter distributions.
	\item We randomly sample Gaussian hop lengths using the
	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
	\item We randomly sampled dwell times from a discrete power law
	distribution based on the reccomendations of Clauset et
	al.~\cite{clauset_power-law_2009}: 
	\begin{equation}
	x = \lfloor
	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
	\label{eqn:discrete_powerlaw_draws}
	\end{equation}
	where $r$ is randomly drawn from a uniform distribution which we simulated
	with \texttt{numpy.random.uniform}.
	\item We found that thermal noise does not significantly influence the MSD and
	therefore did not add any noise to the simulated trajectories. (See supporting info)
  \end{itemize}

  We calculated both the ensemble-averaged and time-averaged mean squared displacements (MSDs)
  of the simulated trajectories.
  \begin{itemize}
	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
	position ~\cite{meroz_toolbox_2015} and can be written as
	\begin{equation}
	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
	\label{eqn:ensemble_msd}
	\end{equation}
	\item The average MSD calculated in this way recovers the form of
	Equation~\ref{eqn:msd_form}. 
	\item The time-averaged MSD measures the displacement between all possible time lags
	and can be written as
	\begin{equation}
	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}{T - \tau} (x(t + \tau) - x(t))^2 dt
	\end{equation}
	where $\tau$ is the time lage and T is the length of the
	trajectory~\cite{meroz_toolbox_2015}. 
	\item The time-averaged MSD becomes linear in our simulations,
	therefore we can fit a line to its slope in order to estimate the macroscopic
	diffusivity of the particle.
	%BJC: this needs more justification. Not many people have done it
	%BJC: could also not report them as diffusivities. Comparison of total MSD
	% should give same information
	% Linear region probably exists because dwell times on the order of large lag times
	% become negligible
  \end{itemize}

  We fixed the length of each simulated trajectory so that we could compare the total
  MSD between different solutes without the influence of the ageing phenomenon.
  \begin{item}
	\item Ageing is defined by the tendency of the average MSD to decrease
	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
	\item The maximum measured dwell time can be no longer than the total length
	of a simulated trajectory. 
	\item As measurement time or trajectory length is increased, longer dwell times
	are incorporated into the calculation, lowering the average MSD. (See supporting
	info for demonstration)
	\item We can achieve consistent total MSDs with low uncertainty for
	simulated trajectories created with a given set of parameters if we fix the
	trajectory length (as opposed to total number of steps).  
  \end{item}

@@

  We quantified the coordination of solutes with surrounding molecules.
  \begin{itemize}
  	\item For each frame, we counted the identites and number of
  	coordinated molecules to a given solute based on a distance cut-off. 
	\item We found that this approach is more useful than calculating the
	3D spherical radial distribution function because it gives detailed
	frame-by-frame information rather than an average. 
  \end{itemize}

@@

  \subsection{Simulated Predictions}\label{section:D_macro}

@@

  Overwhelming amount of water in 10 wt\% system makes hydrogen bonding
  competitive between head groups and water.
  %MRS: not sure what you mean above.

@@

  \clearpage

  \bibliographystyle{ieeetr}
  \bibliography{Transport}
